### 2022-06-21 manuscript/manuscript.Rmd
ms update

When analyzing the motor skills domain we found a significant non-linear effect of corrected age on gross motor scores ($F_{smooth}$ (5.24, 226.75) = 6.19, *p* < 0.001), which had an overall positive effect ($\beta$ = 1.95, CI~95%~[0.66, 3.25], $t_{student}$ (226.75) = 2.97, *p* = 0.003), nevertheless, the slope varied across age, whereas between the 0 to 7 age range this has a negative effect on gross motor score $\beta$ = -2.94, CI~95%~[-4.55, -1.34], $t_{student}$ (226.75) = -3.7, *p* = 0.004, but in the 9.7 to 15.5 a positive effect was observed ($\beta$ = 1.86, CI~95%~[0.61, 3.11], $t_{student}$ (226.75) = 2.93, *p* = 0.009), meanwhile in the 7.3 to 9.2 ($\beta$ = 0.02, CI~95%~[-1.12, 1.17]) and 16 to 48 months old ($\beta$ = -0.02, CI~95%~[-2.05, 2.01]) the slope was non significant and practically cero ($t_{student}$ (226.75) = 0.06, *p* = 0.45, and $t_{student}$ (226.75) = 0.07, *p* = 0.646 respectively).

>>>>

When analysing the motor skills domain, we found a significant non-linear effect of corrected age on gross motor scores ($F_{smooth}$ (5.24, 226.75) = 6.19, *p* < 0.001), which had an overall positive effect ($\beta$ = 1. 95, CI~95%~[0.66, 3.25], $t_{student}$ (226.75) = 2.97, *p* = 0.003), however, the slope varied as a function of age, with a negative effect on gross motor score $\beta$ = -2.94, CI~95%~[-4.55, -1. 34], $t_{student}$$ (226.75) = -3.7, *p* = 0.004, but in the range 9.7 to 15.5 a positive effect was observed ($\beta$ = 1.86, CI~95%~[0.61, 3.11], $t_{student}$ (226.75) = 2.93, *p* = 0.009), while in the range 7.3 to 9.2 ($\beta$ = 0.02, CI~95%~[-1. 12, 1.17]) and 16 to 48 months ($\beta$ = -0.02, CI~95%~[-2.05, 2.01]) the slope was non-significant and virtually zero ($t_{student}$ (226.75) = 0.06, *p* = 0.45, and $t_{student}$ (226.75) = 0.07, *p* = 0.646 respectively).
